---
title: "statcheck on the web // report"
output: pdf_document
params:
  results: NULL
---

```{r setup, include=FALSE}
# Ensure knitr and kableExtra are available
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```

```{=tex}
\begin{center}
  \includegraphics[width=0.5\textwidth]{statcheck-cropped.png}
\end{center}
```
# What is statcheck?

Statcheck is a "spellchecker" for statistics. It searches text for Null Hypothesis Significance Tests (NHST), reported according to the guidelines of the American Psychology Association (APA), and checks if the reported p-values match their accompanying test statistic and degrees of freedom. Statcheck classifies the detected results in one of three categories:

| Classification             | Explanation                                                                                                                               |
|---------------------|---------------------------------------------------|
| **Consistent**             | The reported p-value matches its test statistic and degrees of freedom.                                                                   |
| **Inconsistency**          | The reported p-value does not match its test statistic and degrees of freedom.                                                            |
| **Decision Inconsistency** | The reported p-value is \< .05, whereas the computed p-value based on the test statistic and degrees of freedom is \> .05, or vice versa. |

Please note:

-   statcheck is automated software that can potentially misread or misclassify a result.
-   an inconsistent result can be due to a mistake in a reported p-value, test statistic, degrees of freedom, or a combination of these elements.
-   in some cases, a result is deliberately reported inconsistently (e.g., authors sometimes opt to adjust one element in the reported results to reflect a statistical correction, such as an adjusted p-value instead of a corrected alpha-level in a Bonferroni correction).

We strongly advise against making decisions about a manuscript based solely on a statcheck report.

For more information about what statcheck can and cannot do, please take a look at the FAQ page at <https://statcheck.io>.

# Results

```{r}
# Access the results passed via params
results <- params$results

if (!is.null(results)) {
  # Render the table using kable for PDF output
  kable(results)
} else {
  cat("No results available.")
}


# file name
# version statcheck
# identified for one-tailed tests?
```
