---
title: "statcheck on the web // report"
output: pdf_document
params:
  results: NULL
  file_name: NULL
  date: NULL
  statcheck_version: NULL
  one_tailed: NULL
---

```{r setup, include=FALSE}
# Ensure knitr and kableExtra are available
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(glue)
```

```{=tex}
\begin{center}
\includegraphics[width=0.5\textwidth]{statcheck-cropped.png}
\end{center}
```

------------------------------------------------------------------------

```{r}
results <- params$results

if (nrow(results) > 0) {
  # Compute summary statistics
  total_results <- nrow(results)
  total_consistent <- sum(results$Consistency == "Consistent")
  total_inconsistent <- sum(results$Consistency == "Inconsistency")
  total_dec_inconsistent <- sum(results$Consistency == "Decision Inconsistency")
} else {
  total_results <- total_consistent <- total_inconsistent <- total_dec_inconsistent <- 0
}
```

# Results

**File Name:** `r params$file_name`

**Date:** `r params$date`

**Statcheck Version:** `r params$statcheck_version`

**One-Tailed Test Detection:** `r params$one_tailed`

```{r}
if (nrow(results) > 0) {
  knitr::kable(results, format = "latex", booktabs = TRUE)
} 
```

# Summary
`r if (nrow(results) > 0) paste( "In total, statcheck detected", total_results, "statistical results reported in APA style.", "Of these,", total_consistent, if (total_consistent == 1) "is" else "are", "consistent,", total_inconsistent, if (total_inconsistent == 1) "is" else "are", "inconsistent,", "and", total_dec_inconsistent, if (total_dec_inconsistent == 1) "is" else "are", "a decision inconsistency." )`

`r if (nrow(results) == 0) paste0("**Statcheck did not detect any APA-reported Null Hypothesis Significance Tests.** \\newline \\newline ", "If you think your document does contain tests that statcheck should have picked up, please check if the results are reported completely ", "(i.e., a test statistic, degrees of freedom when applicable, and a p-value) and in APA reporting style. Another common reason why statcheck may not detect results is when there are issues in PDF conversion, in which case you could try uploading the file in HTML or DOCX, if available. \\newline \\newline ", "For more information on what statcheck can and cannot detect, please see the FAQ page at https://statcheck.io.")` 

------------------------------------------------------------------------

\pagebreak

# What is statcheck?

Statcheck is a "spellchecker" for statistics. It searches text for Null Hypothesis Significance Tests (NHST), reported according to the guidelines of the American Psychology Association (APA), and checks if the reported p-values match their accompanying test statistic and degrees of freedom. Statcheck classifies the detected results in one of three categories:

| Classification             | Explanation                                                                                                                               |
|-----------------------|------------------------------------------------|
| **Consistent**             | The reported p-value matches its test statistic and degrees of freedom.                                                                   |
| **Inconsistency**          | The reported p-value does not match its test statistic and degrees of freedom.                                                            |
| **Decision Inconsistency** | The reported p-value is \< .05, whereas the computed p-value based on the test statistic and degrees of freedom is \> .05, or vice versa. |

## Please note

-   statcheck is automated software that can potentially miss, misread or misclassify a result.
-   an inconsistent result can be due to a mistake in a reported p-value, test statistic, degrees of freedom, or a combination of these elements.
-   in some cases, a result is deliberately reported inconsistently (e.g., authors sometimes opt to adjust one element in the reported results to reflect a statistical correction, such as an adjusted p-value instead of a corrected alpha-level in a Bonferroni correction).

***We strongly advise against making decisions about a manuscript based solely on a statcheck report.***

For more information about what statcheck can and cannot do, please take a look at the FAQ page at <https://statcheck.io>.

